---
title: "Introduction"
output: html_document
---

# Team Jet-lag/Topic:COVID-19 Impact

Coronavirus is a hot topic this year, people around the world are hugely affected by it. As international students, we are facing many difficulties due to coronavirus. It affected our lives in so many ways. And we believed that others have been through the same thing like us. 

Thus, we decided to engage in this field and create a website that could help people in this complex situation. We hope that our design could help people gain insights and reduce their stress, informing the public of the effect of COVID-19 on education, transportation, and work. We also want to go further by adding information about where you could get a covid test and which hospital you could go to for help. 



## Summary Information




## Table





## Chart 1
```{r include = FALSE}
source("script/Chart_race_hosp.R")
```
Due to the sudden mass out broke of the pandemic, hospital resources became 
preciouses and not everyone had the opportunity to be treated by hospitals. We
want see whether there is a difference in hospital treatment rate among people 
from different race and ethnicity groups by looking into the general hospital
treatment rate of COVID-19 in the U.S. and comapre it with the hospital 
treatment rates for each specific race and ethnicity group.

The chart showing the hosipital treatment rate among different race and 
ethnicity is displayed below.
(People who do not have a hospital reocord and people who have a unknown race
and ethnicity record are filtered out from the data.)
```{r}
race_hosp_chart
```
According to the chart, we can see that the over all hospital treatment among 
all race and ethnicity is `r format(hosp_y * 100，digits = 1) `%, which is 
rather low. This may be a sign indicating how compacked hospitals are and the 
inability of hospitals for taking in all patients in need. Among all race and
ethnicity groups, black and non-hispanic people have a hospotal treatment rate 
of `r format(hosp_y_max * 100, digits = 1 )`%, which is the highest among all 
race and ethnicity groups. The race and ethnicity that have the lowest hospital
treatment rate is Native Hawaiian/Other Pacific Islander and non-hispanic 
people, `r format(hosp_y_min * 100, digits = 1 )`%. Possible explaination of 
these differences may be variation in ability to pay for hospital treatment, 
severity of illness, and the willingness to seek hospital treatment among these
groups.



## Chart 2
```{r include = FALSE}
source("script/chart_2.R")
```
Since so many people have been unfortunately confirmed to be the carrier of COVID-19, the public went into panic at the beginning of this chaos. Numerous people are still wondering what the age group of people COVID-19 normally targets at, thus we hope to generate a chart to display the statistical information about the confirmed-cases age group, informing the public an potential correlation between age and the possibility of getting COVID-19.

Below is a chart showing the percentage of confirmed cases by age group and gender:
```{r}
age_plot
```

Based on this chart, we can easily observe that most of COVID-19 cases are confirmed at the age group between `r most_age`, which takes up about `r format(most_percent * 100, digits = 1 )`% of the total confirmed population. On the other hand, the age group `least_age` has the smallest percentage of confirmed cases that takes up only about `format(least_percent * 100, digits = 1 )`%. From this chart, we can see that the majority of confirmed cases are founded in the age group above 30 years old, which might indicate that there is a positive correlation between the possibility of getting COVID-19 and the age of individuals.



## Chart 3

```{r include = FALSE}
source("script/Chart_3_Covid-19 cases mortality rates for every sex in each age group")
```
Covid-19 is getting very serious in the United States, but fortunately, the death rate for this pandemic
is relatively lower than other serious pandemic. But what kind of group has a higher mortality rate? Is
ther any connection between gender and mortality rates or age and mortality rates? Thus, we would like to 
use this graph to find out how gender influence the mortality rates ofpeople in each age group.

Based on the chart, we could see that gender and age did have impact on the mortality rates. We could see 
that the mortality rates are nearly 0% for people from 0-29 years old. However, the mortality rates keep 
increased as age increased. And `r format(max_M,nsmall=2)`is the highest mortality rates for male, `r format(max_M_A)`
is the age group with highest mortality rate for male. `r format(max_F,nsmall=2)`is the highest mortality rates for
female,and `r format(max_F_A)`age group with highest mortality rate for female. We could learn that before 75 years old,
male has higher mortality rates than female. However, after 75 years old, female has high mortality rates than male. 
And one interesting things I found in this chart is that peopel who have "other" gender identity has almost 0% mortality
rate in every age group. 




